SAT Competition 2020\tnoteref{title}

### 2020-12-27 paper/main.tex
refined incremental and kissat

\section{History of Code and Winning Strategies}
\label{sec:analysis}

@@

\subsection{Sequential SAT Solving: Winners of the Main and Incremental Tracks}
\label{sec:part:seq}

A total of $18$ teams submitted their solvers to the main track of the competition.  
Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
$14$ teams submitted variants of a previously existing base solver such as Maple~\cite{} or CaDiCaL~\cite{}.

In the incremental track, four teams submitted their solvers. 
All solvers in the incremental library track are created from independent code bases. 
Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers.

@@

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solbert{trail} & \secondu\\
 &  &  \solbert{alluip} & \secondu, \firstp\\
 & \multirow{-3}{*}{\solbert{CaDiCaL}} &  \solver{alluip-trail} & \secondu, \firstp\\
 \cline{2-4}
 & \solbert{MapleLCMDist} & \solver{alluip-trail} & \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solbert{MapleLCMDistCBT}} & \solver{f2trc} & \thirdu\\
 & & \solbert{f2trc-s} & \thirdu\\
 \cline{2-4}
 & \solbert{MapleLCMDistCBT-DL} & \solver{f2trc} & \thirdu\\
\hline

@@

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solver{ParaFROST}} & -- & \\
 &  & \solbert{CBT} & \\
\hline
\end{tabular}
\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: In favour of highlighting the relevant branch in the Maple tree of solvers, we identify configuration names of solvers, as well as variants of other base solvers in Column~3 ``Variant / Name''. To avoid confusion, we \solver{underlined} the names of the submitted solvers.}
\label{tab:solvers-main}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & CaDiCaL-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
\label{tab:solvers-incremental}
\end{table}

@@

If it came to determine an overall winner of all the subtracks in the Main Track of this competition, then it would clearly be Kissat. 
Kissat was submitted in three configurations, including one default configuration and specialized configurations specifically tailored towards satisfiable or unsatisfiable instances, respectively.
Kissat won four awards, by achieving first place in the overall Main Track, first place in its Unsat Sub-Track, second place in the Sat Sub-Track and third place in the Planning Sub-Track.

Kissat is a reimplementation of CaDiCaL~\cite{Biere:SC2019} in C, thus, taking advantage of finegrained control on the memory layout of new sophisticated data-structures used to manage watchers and clauses, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2020}.

In Kissat, forward subsumption for learned clauses was entirely replaced by more powerful vivification algorithms~\cite{ChuMinLi:2020:Vivification}. 
For irredundant clauses, forward subsumption is still executed together with variable elimination during pre- and inprocessing, but only in a very focused way, by carefully monitoring variable occurrences~\cite{Biere:SC2020}.

Kissat also comes with a refined scheduling of inprocessing procedures based on growing conflict intervals. 
Regarding the duration of alternating restart modes, Kissat's author considered conflict-rate being too unstable, and come up with ``ticks'', which is a new method to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses.

Considering target phases~\cite{Biere:SC2019}, Kissat's author come up with an innovative use-case for autarkies to account for saved phases. 
Before each rephasing step they compute the largest autarky of the full assignment with an algorithm described in~\cite{Kiesl:2019:Autarkies}. 
The authors claim this autarky contains satisfying assignments of disconnected components which otherwise would get lost, and thus next, they are considered in variable elimination.

>>>>

\section{Code-Bases and Winning Strategies}
\label{sec:analysis}

@@

\subsection{Sequential SAT Solving}
\label{sec:part:seq}

Sequential SAT solvers have been evaluated in the Main tracks as well as in the Incremental track of SAT Competition~2020. 
A total of $18$ teams submitted correct solvers to the Main track of the competition. 
Table~\ref{tab:solvers-main} displays an overview of the participating teams, base solvers and their variants. 
The recent genealogy of all submissions, is highlighted by \emph{base solver} and \emph{variant} columns. 
Underlined text is used to point out the important parts of the respective submissions name.

@@

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solbert{trail} & \secondu\\
 &  &  \solbert{alluip} & \secondu, \firstp\\
 & \multirow{-3}{*}{\solbert{CaDiCaL}} &  \solver{alluip-trail} & \secondu, \firstp\\
 \cline{2-4}
 & \solbert{MapleLCMDist} & \solbert{alluip-trail} & \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solbert{MapleLCMDistCBT}} & \solver{f2trc} & \thirdu\\
 & & \solbert{f2trc-s} & \thirdu\\
 \cline{2-4}
 & \solbert{MapleLCMDistCBT-DL} & \solbert{f2trc} & \thirdu\\
\hline

@@

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solver{ParaFROST}} & -- & \\
 &  & \solbert{CBT} & \\
\hline
\end{tabular}
\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: Column~2 highlights the recent genealogy of submissions and Column~3 displays configuration names as well as names of forks. We partially \solver{underlined} submission names. Awards in the Main- (M), Planning- (P), Sat- (s), and Unsat- (u) Tracks are indicated by a string TX with $T \in \{M, P, s, u\}$ and $X \in \{1,2,3\}$. }
\label{tab:solvers-main}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Four submissions made it to participate in the Incremental Library track, some of which, e.g, \solver{CryptoMinisat-5}, have also been evaluated and awarded in the Main sequential track. 
Submissions to the Incremental Library track have been evaluated with respect to $6$ different applications -- each with $50$ benchmark instances. 
Table~\ref{tab:solvers-incremental} displays an overview of the participating teams and solvers. 
In this table, \emph{Score} denotes the number of application categories in which the solvers won based on their PAR-2 score.

\begin{table}[ht]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fleury}~ & CaDiCaL-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption[Teams and Solvers in the Incremental Track]{Teams and Solvers in the Incremental Library Track: Score indicates the amount of application categories won with the submission.}
\label{tab:solvers-incremental}
\end{table}

@@

Three major configurations of \solver{Kissat} were evaluated in this competition. 
That includes one default configuration and two specialized configurations which are specifically tailored towards satisfiable and unsatisfiable instances, respectively. 
\solver{Kissat} won \emph{four awards}, by achieving first place in the Main track, first place in the Unsat track, second place in the Sat track and third place in the Planning track.

\solver{Kissat} is a reimplementation of \solver{CaDiCaL} in C,
but comes with new sophisticated lazy data-structures for clause state monitoring, e.g., through binary clause inlining, sentinel values and bit stuffing~\cite{Biere:SC2019,Biere:SC2020}. 
Moreover, forward subsumption for learned clauses is mostly replaced by vivification algorithms~\cite{ChuMinLi:2020:Vivification}.

\solver{Kissat} uses a new unit (``ticks'') to measure the length of two alternating restart-modes based on the approximate number of cache-line accesses, after conflict-rate has been obeserved to be too unstable for the use-case~\cite{Biere:SC2020}.

\solver{Kissat} also exploits an innovative use-case for autarkies to account for saved phases. 
In order to keep valuable information of saved phases, before each rephasing step, \solver{Kissat} computes the largest autarky for the assignment implied by the current saved phases~\cite{Kiesl:2019:Autarkies}. 
As such an autarky might contain satisfying assignments which imply disconnected components, those variables are subject to subsequent variable elimination.
